Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-16 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Reviewing English grammar from experiments. Minor changes

\section{Enhancing NodIO with a Web Worker-based architecture}
\label{sec:w2}

@@

This experiment was deployed in a virtual private server with 512MB of memory
running Ubuntu OS version 14.04 and hosted in DigitalOcean.com. Unlike previous
experiments where the optimum was expected to be found many times, 
this problem was expected to run constantly for many days finding only
sub-optimal approximations. In order to achieve this, the only change needed 
in the framework was to limit the number of chromosomes kept in the pool. 
Previously, every PUT request which included a new chromosome increased 
the size of the pool, in a long-running experiment this has to be avoided
in order to not exhaust the available memory. In this experiment the size
of a chromosome was 1000 double precision numbers, considering this
and the memory available in the server, the the pool was limited 
to 10,000 chromosomes.  In order to keep this size
constant a random chromosome was pulled out of the pool before inserting a
new one, when the pool was full. For this problem {\sf NodEO}'s {\tt chromosome-float} 
and {\tt classic-ea-float} modules were used. The parameters for the EA 
were tournament size = 3 and  population size = 500, returning exchanging a
chromosome with the server every 100 generations. Again two workers in each window.
As before, a few participation calls were published in social networks.

@@

There are several validity threats to the design of this study.
Participants of the experiments were mainly members of our 
own social networks, personal colleagues, friends 
and acquaintances, when extending this work other options 
should be considered in order to include 
a wider audience with different motives for participation.
Another threat is that participants were anonymous so the amount of repeated 
participations and the effects this had in the outcome is not
known. Another issue is that the scalability of the system was not thoroughly tested
but for the amount of participants the basic configuration 
was more than adequate, again more experiments are needed in order
to assess the capability both with more clients and other server
configurations. Although care was taken to include representative benchmarks
of real world problems, more experiments with a broader coverage 
should allow a better understanding of the practical limitations of
the architecture and the tools chosen.

>>>>

\section{Enhancing {\sf NodIO} with a Web Worker-based architecture}
\label{sec:w2}

@@

This experiment was deployed in a virtual private server with 512MB of memory
running Ubuntu OS version 14.04 and hosted in DigitalOcean.com. Unlike previous
experiments where the optimum was expected to be found many times, 
this problem was expected to run constantly for many days finding only
sub-optimal approximations. In order to achieve this, the only change needed 
in the framework was to limit the number of chromosomes kept in the pool. 
Previously, every PUT request which included a new chromosome increased 
the size of the pool. But in a long-running experiment this has to be avoided
in order to not exhaust the available memory. In this experiment the size
of a chromosome was 1000 double precision numbers, so that considering this
and the memory available in the server, the pool was limited 
to 10,000 chromosomes.  In order to keep this size
constant, a random chromosome was pulled out of the pool before inserting a
new one, when the pool was full. For this problem {\sf NodEO}'s {\tt chromosome-float} 
and {\tt classic-ea-float} modules were used. The parameters for the EA 
were tournament size = 3 and  population size = 500, returning exchanging a
chromosome with the server every 100 generations. Again, there were two workers in each window.
As before, a few participation calls were published in social networks.

@@

% (Paloma) Mario, isn't this the future work? Should it be in conclusions? If not, just ignore this comment.
There are several validity threats to the design of this study.
Participants of the experiments were mainly members of our 
own social networks, personal colleagues, friends 
and acquaintances, therefore to extend this work other options 
should be considered in order to include 
a wider audience with different motives for participation.
Another threat is that participants were anonymous so the amount of repeated 
participations and the effects this might have had in the outcome is not
known. Another issue is that the scalability of the system was not thoroughly tested
but for the amount of participants the basic configuration 
was more than adequate, then again more experiments are needed in order
to assess the capability both with more clients and other server
configurations. Although care was taken to include representative benchmarks
of real world problems, more experiments with a broader coverage 
should allow a better understanding of the practical limitations of
the architecture and the tools chosen.
